A Framework for Equivalence of Cast Calculi and a new Cast Representation

### 2020-10-09 paper.tex
Updates from Overleaf

% functions
\newcommand{\meet}[2]{\ensuremath{#1 \sqcap #2}}
\newcommand{\denote}[1]{\ensuremath{\llbracket #1 \rrbracket}}
\newcommand{\proxy}[2]{\ensuremath{\mathrm{proxy}(#1,#2)}}
\newcommand{\applyCast}[2]{\ensuremath{\mathrm{applyCast}(#1,#2)}}
\newcommand{\project}[4]{\ensuremath{\mathrm{project}(#1,#2,#3,#4)}}
\newcommand{\composegap}[3]{\ensuremath{#1 \fatsemi #2 \fatsemi #3}}
\newcommand{\mkhead}[2]{\ensuremath{\mathrm{mkProj}(#1,#2)}}
\newcommand{\mktail}[2]{\ensuremath{\mathrm{mkInj}(#1,#2)}}
\newcommand{\mkgap}[3]{\ensuremath{\mathrm{mkGap}(#1,#2,#3)}}
\newcommand{\compose}[2]{\ensuremath{#1 \fatsemi #2}}
\newcommand{\translate}[1]{\ensuremath{\lceil#1\rceil}}
\newcommand{\castToDyn}[2]{\ensuremath{\mathrm{castToDyn}(#1,#2)}}
\newcommand{\castFromDyn}[2]{\ensuremath{\mathrm{castFromDyn}(#1,#2)}}
\newcommand{\dom}[1]{\ensuremath{\mathrm{dom}(#1)}}
\newcommand{\cod}[1]{\ensuremath{\mathrm{cod}(#1)}}
\newcommand{\fst}[1]{\ensuremath{\mathrm{fst}(#1)}}
\newcommand{\snd}[1]{\ensuremath{\mathrm{snd}(#1)}}
\newcommand{\id}[1]{\ensuremath{\mathrm{id}(#1)}}
\newcommand{\idm}[1]{\ensuremath{\mathrm{id}_m(#1)}}
\newcommand{\idc}[1]{\ensuremath{\mathrm{id}_c(#1)}}
\newcommand{\mkContName}[0]{\ensuremath{\mathrm{mkK}}}
\newcommand{\mkCont}[1]{\ensuremath{\mkContName(#1)}}
\newcommand{\extContName}[0]{\ensuremath{\mathrm{extK}}}
\newcommand{\extCont}[2]{\ensuremath{\extContName(#1,#2)}}
% \newcommand{\applyCont}[2]{\ensuremath{\langle\langle#1,#2\rangle\rangle}}
\newcommand{\applyContName}[0]{\ensuremath{\mathrm{applyK}}}
\newcommand{\applyCont}[2]{\ensuremath{\applyContName(#1,#2)}}

% other relations
\newcommand{\tailable}[2]{\ensuremath{\casttyping{!}{#1}{#2}}}
\newcommand{\consistent}[2]{\ensuremath{#1\sim#2}}
\newcommand{\shallowlyconsistent}[2]{\ensuremath{#1\smile#2}}
\newcommand{\notshallowlyconsistent}[2]{\ensuremath{#1\not\smile#2}}
\newcommand{\expressiontyping}[3]{\ensuremath{#1 \vdash #2 : #3}}
\newcommand{\matching}[2]{\ensuremath{#1 \triangleright #2}}
\newcommand{\valuetyping}[2]{\ensuremath{\vdash #1 : #2}}
\newcommand{\envtyping}[2]{\ensuremath{#1 \vdash #2}}
\newcommand{\casttyping}[3]{\ensuremath{\vdash #1 : #2 \Longrightarrow #3}}
\newcommand{\transitivelyreducetoM}[3]{\ensuremath{#2 \longmapsto_{#1}^{*} #3}}
\newcommand{\transitivelyreduceto}[2]{\ensuremath{#1 \longmapsto^{*} #2}}
\newcommand{\transitivelyreducetoD}[2]{
	\ensuremath{#1 \longmapsto_{\LDMachine}^{*} #2}}
\newcommand{\transitivelyreducetoUD}[2]{
	\ensuremath{#1 \longmapsto_{\LUDMachine}^{*} #2}}
\newcommand{\reduceto}[2]{\ensuremath{#1 \longmapsto #2}}
\newcommand{\reducetoR}[3]{\ensuremath{#2 \longmapsto_{\CMachine{#1}} #3}}
\newcommand{\reducetoD}[2]{\reducetoR{\BLD}{#1}{#2}}
\newcommand{\reducetoUD}[2]{\reducetoR{\BLUD}{#1}{#2}}
\newcommand{\reducetoS}[3]{\ensuremath{#2 \longmapsto_{\SMachine{#1}} #3}}
\newcommand{\evalto}[2]{\ensuremath{\mathit{eval}(#1)=#2}}
\newcommand{\withmachineevalto}[3]{\ensuremath{\mathit{eval}_{#1}(#2)=#3}}
\newcommand{\evaltoR}[3]{\ensuremath{\mathit{eval}_{\CMachine{#1}}(#2)=#3}}
\newcommand{\evaltoD}[2]{\evaltoR{\BLD}{#1}{#2}}
\newcommand{\evaltoUD}[2]{\evaltoR{\BLUD}{#1}{#2}}
\newcommand{\evaltoS}[3]{\ensuremath{\mathit{eval}_{\SMachine{#1}}(#2)=#3}}
\newcommand{\compatibletailhead}[2]{\ensuremath{#1\;\mathit{R}\;#2}}
\newcommand{\goodgap}[1]{\ensuremath{\mathit{good}(#1)}}
\newcommand{\compileto}[4]{\expressiontyping{#1}{#2\rightsquigarrow#3}{#4}}
\newcommand{\machineequiv}[2]{
	\ensuremath{
		\withmachineevalto{#1}{e}{o}	
		\text{ if and only if }
		\withmachineevalto{#2}{e}{o}
		\text{ for all }
		\expressiontyping{\emptyset}{e}{T}
		\text{ and }
		\valuetyping{o}{T}
	}}
\newcommand{\bisimE}[3]{\ensuremath{#1 \vdash #2 \approx #3}}
\newcommand{\bisimv}[3]{\valuetyping{#1 \approx #2}{#3}}
\newcommand{\bisimr}[3]{\valuetyping{#1 \approx #2}{#3}}
\newcommand{\bisimF}[4]{\casttyping{#1 \approx #2}{#3}{#4}}
\newcommand{\bisimc}[4]{\casttyping{#1 \approx #2}{#3}{#4}}
\newcommand{\bisimK}[4]{\casttyping{#1 \approx #2}{#3}{#4}}
\newcommand{\bisims}[3]{\valuetyping{\ensuremath{#1 \approx #2}}{#3}}

\begin{document}
%
\title{A Framework for Equivalence of Cast Calculi and a new Cast Representation}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Kuang-Chen Lu\inst{1} \and
Jeremy G. Siek\inst{2} \and
Andre Kuhlenschmidt\inst{2}
}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Brown University, Providence RI 02912, USA \and
Indiana University, Bloomington IN 47405, USA}
% \institute{Princeton University, Princeton NJ 08544, USA \and
% Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
% \email{lncs@springer.com}\\
% \url{http://www.springer.com/gp/computer-science/lncs} \and
% ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
% \email{\{abc,lncs\}@uni-heidelberg.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Gradual typing aims at combining dynamic typing and static typing in one 
language to provide the advantages of both typing disciplines. Implementing 
gradual typing with reasonable overhead, however, is not trivial. Casts might 
accumulate in higher-order values and continuations, thus change the overall 
space complexity. Several space-efficient cast representations have been 
proposed, notably coercions in normal forms and threesomes. But they are
presented in different dynamic semantics, which make it difficult to compare
the key differences between the cast representations. We present a abstrat
data type, namely Cast ADT, that captures interface functions a cast representations
typically includes, and an abstract machine parameterized over Cast ADTs.
The Cast ADT brings another benefit: space-efficient cast representations 
shall be proved not changing the 
overall behavior of language implementations except saving space.
With our generic abstract machine, these proofs can be done by proving properties
of a specific Cast ADT, which is simpler than going through a bisimulation proof 
between a space-efficient dynamic semantics and the definitional dynamic semantics.
We have successfully applied our new approach of proving the correctness of cast 
representations to several known cast representations and believe this framework
is also applicable to other cast representations.
\todo[inline]{JS: cite which other cast representations}
We also present a new cast representation, hypercoercions, that is more friendly
to mechanized meta-theory and consumes less memory than coercions
in normal forms.

@@

\todo[inline]{KC: Cite "Contracts for higher-order functions" for the proxy-based approach maybe?}
\todo[inline]{JS: That paper doesn't exactly fit into what you're talking about in the above
sentence. It might be appopriate to cite it elsewhere in the paper. Also,
there are earlier papers about coercive subtyping (Computing with coercions by Breazu-Tannen et al)
that use a proxy-based approach. The contracts paper may be the first to propose blame tracking.}
\todo[inline]{KC: I think readers should be able to trace back history by following the pointers in the 
intro section. I don't know whether my thought is correct. I would rather not giving misleading
pointers. I also don't know how far should a pointer chases back. Readers can be directed to recently
works which will eventually lead them back to the earliest possible paper. But wouldn't it be
great if the author of a new paper shows reader all the milestones? After all we already know 
pointer dereferencing is expensive.}
\todo[inline]{JS: Yes, citing the original paper for each idea is great.
  I'm just saying 1) cite the correct paper for each idea and 2)
  talk about the various ideas in an organized way with respect
  to your sentence and paragraph structure.}

Gradual typing \citep{siek2006gradual,siek2015refined} includes both static typing 
and dynamic typing in the same language and enables a smooth transition between them while
enforcing type soundness.
To enable a smooth transition, gradually typed languages feature a special type
typically written as \Tdyn{}, \lstinline|Dyn|, or \lstinline|Any|, which
provides a way to write imprecise type annotations. A gradual type checker allows programmers to cast 
implicitly between types that have no conflicting type information.
At runtime, casts record and check type information to enforce type soundness.
Researchers often define the semantics of gradually typed languages by
translation to an intermediate language with explicit casts, such as the blame
calculus \citep{wadler2009well} and other cast calculi \citep{siek2009exploring}.
% To allow the smooth transition, every gradually typed language
% has a special type typically written as \Tdyn\ or \lstinline|Dyn| or \lstinline|Any|,
% which enables imprecise type annotations.
% Programmers can use an expression of type \texttt{T} in any context that \texttt{T} 
% is consistent to.
% Two types are consistent if they have no conflicting type information.
% For instance, \lstinline|(->  Bool Int)| is consistent with \lstinline|(->  $\star$ Int)| but
% not consistent with \lstinline|(->  Int Int)|.
% When the type of an expression is consistent but not equal to the type of its 
% context, there would be a runtime computation (i.e. a cast) that store or check 
% type information to enforce type soundness.

@@

@@

\citet{siek2020mechanized} defines two dynamic semantics for 
cast calculi parameterized over cast representations, similar to
our \CMachine{B}. The two corresponding interfaces, namely
$\mathrm{CastStruct}$ and $\mathrm{EfficientCastStruct}$, give
users more control over the structure of values. \CMachine{B} machine
insists that the cast on the top of a value must be a function cast
or a product cast. In contrast, users of their interfaces define
a predicate on casts called $\mathrm{Inert}$ and any inert cast can
be a part of a value. Their system doesn't include theorems relating
space-inefficient cast calculi and space-efficient ones, which
is one of the major goals of our framework.

% We review closely related work in three areas: coercions in normal
% form, threesomes, and parameterized cast calculi.

\subsubsection{Coercions in normal form}

\citet{henglein1994dynamic} introduces coercions to study compilation
from dynamic languages to statically typed
ones. \citet{herman2010space} proposes using coercions in normal forms
to represent casts in gradual typing and proves space efficiency.
However, they did not prove that the coercion-based semantics is
equivalent to the standard (and type-based)
one. \citet{Siek:2015:BCT:2737924.2737968} improve the Lazy UD style
of coercions in normal forms and prove that Lazy UD coercions in
normal form are correct, using two bisimulation between three
reduction semantics. The first semantics is similar to \LUDMachine,
which bisimulates a reduction semantics using coercions (not
necessarily in normal form). The last semantics uses coercions in
normal form and bisimulates the coercions-based semantics.

\todo[inline]{KC: [IMPORTANT]}
\todo[inline]{JS: say something about the difference between the above
  and what is in this paper. That's the whole point of the related
  work section from the eyes of the reviewer.}
\todo[inline]{KC: I might have some misconcept about the related work section.
You might have felt this, haha. Now I think this section is targeting the
following scenarios: 
- ``I think someone has solved this problem ...''
- ``This work looks similar to paper X, what is the difference?''
- ``Is this work inspired by paper X?''
Is my understanding correct?}
\todo[inline]{JS: yes, and make sure to
  give very explicit answers to these questions. It should feel to you
  like you're hitting the reader over the head with the most obvious
  things (to you). The above paragraph is currently insufficient
  because it doesn't emphasize what scientific constributions are new
  to our paper compared to those prior papers on coercions in normal
  form.}

\subsubsection{Threesomes}

\citet{Siek:2010:TWB:1706299.1706342} introduce Lazy UD threesomes and
prove them correct, using a bisimulation between two reduction
semantics: one is analogous to the \LUDMachine; the other uses Lazy UD
threesomes and is analogous to the machine in
Section~\ref{sec:framework}.  \citet{Garcia:2013:CTB:2500365.2500603}
introduces several other flavors of threesomes, including a Lazy D
one. Their threesomes are derived from the corresponding styles of
coercions in normal form, using correctness-preserving
transformation. So the correctness of their threesomes relies on the
correctness of the coercions-in-normal-form-based semantics defined in
\citet{herman2010space}, which has not been proved correct.

\todo[inline]{JS: again, say something about the difference between
  the above and what is in this paper.}
\todo[inline]{KC: [IMPORTANT] will do.}

\subsubsection{Parameterized cast calculi}

@@

\todo[inline]{JS: The above is too short of a description of that related
work.}

@@

The syntax \error{l} occurs several times in the syntax definition. We shall 
view those nonterminals that have an \error{l} case as error monads. We use 
the symbol \mbind{} as the monad bind operator, which is defined as follows:
\[
\begin{array}{rcll}
(\error{l}) \mbind f & = & \error{l} \\
          a \mbind f & = & f(a)      & \text{otherwise}
\end{array}
\]
\todo[inline]{JS: why not use monadic let instead? That avoids
  the need to also use meta-lambdas, which you would need to
  explain, e.g., in the transition rule that uses applyCast.}
\todo[inline]{KC: 1. I will try to switch to monadic let. As you pointed out
when we wrote the WGT paper, let is more friendly to readers who are not familiar
with monads.
2. Do you imply that monadic let doesn't need to be explained?
}
\todo[inline]{JS: No, you should still define monadic let.}

@@

The transition relation \reduceto{s}{s} invokes the cast application
function, noted as $\applyCast{v}{\ccast{S}{l}{T}}$, which is also defined
by specify blame strategies (Fig.~\ref{fig:blame-strategy-LazyD} and
Fig.~\ref{fig:blame-strategy-LazyUD}).
\todo[inline]{JS: be consistent with the font used for applyCast. Sometimes
  you use roman and sometimes you used italic. Also, be consistent
  for all the metafunctions (eval, observe, etc.).}
\todo[inline]{KC: [IMPORTANT] will do.}
%
When evaluating a cast expression, the machine moves the cast to the
continuation and evaluates the inner expression.
%
To cast a value, the machine invokes applyCast on the value. The cast
result is either a value or an error (\error{l}). If the cast
succeeds, the machine returns the value to the next continuation.  If
the cast fails, the machine halts with the blame label.
%
To apply a casted function, the machine first casts the argument $v$, then
applies the inner function $u$ to the casted argument, and finally
casts the return value.
%
To project the first element of a casted pair, the machine projects
the first element of the inner pair $u$ and cast it.
%
Projecting the second element of a casted pair is similar.

@@

\fbox{$\mathit{applyCast}_{\BLD}(v,\ccast{S}{l}{T}) = r$}
\[
\begin{array}{rclr}
\figequalto{
	applyCast(v,\ccast{\Tdyn}{l}{\Tdyn})
}{
	\just{v}
}{}
\figequalto{
applyCast(v,\ccast{P}{l}{\Tdyn})
}{
	\just{\vdyn{P}{v}}
}{}
\figequalto{
	applyCast(\vdyn{P}{u},\ccast{\Tdyn}{l}{Q})
}{
	applyCast(u,\ccast{P}{l}{Q})
}{}
\figequalto{
	applyCast(v,\ccast{P}{l}{Q})
}{
	\just{\proxy{v}{\ccast{P}{l}{Q}}}
}{\sidecond{\shallowlyconsistent{P}{Q}}}
\figequalto{
	applyCast(v,\ccast{P}{l}{Q})
}{
	\error{l}
}{\sidecond{\notshallowlyconsistent{P}{Q}}}
\end{array}
\]
\caption{The \LD\ blame strategy (\BLD)}
\label{fig:blame-strategy-LazyD}
\end{figure}

\todo[inline]{KC: conditions of blame strategy}
\begin{definition}[Blame Strategy, $B$]
A blame strategy defines a subset of pre-types, written I, that is injectable,
and a function, written applyCast, that applies cast to values.
\end{definition}

@@

@@

\todo[inline]{JS: There should be some text regarding the following
two theorems.}

>>>>

% functions
\newcommand{\meet}[2]{\ensuremath{#1 \sqcap #2}}
\newcommand{\denote}[1]{\ensuremath{\llbracket #1 \rrbracket}}
\newcommand{\proxy}[2]{\ensuremath{\mathrm{proxy}(#1,#2)}}
\newcommand{\applyCast}[2]{\ensuremath{\mathrm{applyCast}(#1,#2)}}
\newcommand{\project}[4]{\ensuremath{\mathrm{project}(#1,#2,#3,#4)}}
\newcommand{\composegap}[3]{\ensuremath{#1 \fatsemi #2 \fatsemi #3}}
\newcommand{\mkhead}[2]{\ensuremath{\mathrm{mkProj}(#1,#2)}}
\newcommand{\mktail}[2]{\ensuremath{\mathrm{mkInj}(#1,#2)}}
\newcommand{\mkgap}[3]{\ensuremath{\mathrm{mkGap}(#1,#2,#3)}}
\newcommand{\compose}[2]{\ensuremath{#1 \fatsemi #2}}
\newcommand{\translate}[1]{\ensuremath{\lceil#1\rceil}}
\newcommand{\castToDyn}[2]{\ensuremath{\mathrm{castToDyn}(#1,#2)}}
\newcommand{\castFromDyn}[2]{\ensuremath{\mathrm{castFromDyn}(#1,#2)}}
\newcommand{\dom}[1]{\ensuremath{\mathrm{dom}(#1)}}
\newcommand{\cod}[1]{\ensuremath{\mathrm{cod}(#1)}}
\newcommand{\fst}[1]{\ensuremath{\mathrm{fst}(#1)}}
\newcommand{\snd}[1]{\ensuremath{\mathrm{snd}(#1)}}
\newcommand{\id}[1]{\ensuremath{\mathrm{id}(#1)}}
\newcommand{\idm}[1]{\ensuremath{\mathrm{id}_m(#1)}}
\newcommand{\idc}[1]{\ensuremath{\mathrm{id}_c(#1)}}
\newcommand{\mkContName}[0]{\ensuremath{\mathrm{mkK}}}
\newcommand{\mkCont}[1]{\ensuremath{\mkContName(#1)}}
\newcommand{\extContName}[0]{\ensuremath{\mathrm{extK}}}
\newcommand{\extCont}[2]{\ensuremath{\extContName(#1,#2)}}
% \newcommand{\applyCont}[2]{\ensuremath{\langle\langle#1,#2\rangle\rangle}}
\newcommand{\applyContName}[0]{\ensuremath{\mathrm{applyK}}}
\newcommand{\applyCont}[2]{\ensuremath{\applyContName(#1,#2)}}
\newcommand{\applyCastName}[0]{\ensuremath{\mathrm{applyCast}}}

% other relations
\newcommand{\tailable}[2]{\ensuremath{\casttyping{!}{#1}{#2}}}
\newcommand{\consistent}[2]{\ensuremath{#1\sim#2}}
\newcommand{\shallowlyconsistent}[2]{\ensuremath{#1\smile#2}}
\newcommand{\notshallowlyconsistent}[2]{\ensuremath{#1\not\smile#2}}
\newcommand{\expressiontyping}[3]{\ensuremath{#1 \vdash #2 : #3}}
\newcommand{\matching}[2]{\ensuremath{#1 \triangleright #2}}
\newcommand{\valuetyping}[2]{\ensuremath{\vdash #1 : #2}}
\newcommand{\envtyping}[2]{\ensuremath{#1 \vdash #2}}
\newcommand{\casttyping}[3]{\ensuremath{\vdash #1 : #2 \Longrightarrow #3}}
\newcommand{\transitivelyreducetoM}[3]{\ensuremath{#2 \longmapsto_{#1}^{*} #3}}
\newcommand{\transitivelyreduceto}[2]{\ensuremath{#1 \longmapsto^{*} #2}}
\newcommand{\transitivelyreducetoD}[2]{
	\ensuremath{#1 \longmapsto_{\LDMachine}^{*} #2}}
\newcommand{\transitivelyreducetoUD}[2]{
	\ensuremath{#1 \longmapsto_{\LUDMachine}^{*} #2}}
\newcommand{\reduceto}[2]{\ensuremath{#1 \longmapsto #2}}
\newcommand{\reducetoR}[3]{\ensuremath{#2 \longmapsto_{\CMachine{#1}} #3}}
\newcommand{\reducetoD}[2]{\reducetoR{\BLD}{#1}{#2}}
\newcommand{\reducetoUD}[2]{\reducetoR{\BLUD}{#1}{#2}}
\newcommand{\reducetoS}[3]{\ensuremath{#2 \longmapsto_{\SMachine{#1}} #3}}
\newcommand{\evalto}[2]{\ensuremath{\mathrm{eval}(#1)=#2}}
\newcommand{\withmachineevalto}[3]{\ensuremath{\mathrm{eval}_{#1}(#2)=#3}}
\newcommand{\evaltoR}[3]{\ensuremath{\mathrm{eval}_{\CMachine{#1}}(#2)=#3}}
\newcommand{\evaltoD}[2]{\evaltoR{\BLD}{#1}{#2}}
\newcommand{\evaltoUD}[2]{\evaltoR{\BLUD}{#1}{#2}}
\newcommand{\evaltoS}[3]{\ensuremath{\mathrm{eval}_{\SMachine{#1}}(#2)=#3}}
\newcommand{\compatibletailhead}[2]{\ensuremath{#1\;R\;#2}}
\newcommand{\goodgap}[1]{\ensuremath{\mathrm{good}(#1)}}
\newcommand{\compileto}[4]{\expressiontyping{#1}{#2\rightsquigarrow#3}{#4}}
\newcommand{\machineequiv}[2]{
	\ensuremath{
		\withmachineevalto{#1}{e}{o}	
		\text{ if and only if }
		\withmachineevalto{#2}{e}{o}
		\text{ for all }
		\expressiontyping{\emptyset}{e}{T}
		\text{ and }
		\valuetyping{o}{T}
	}}
\newcommand{\bisimE}[3]{\ensuremath{#1 \vdash #2 \approx #3}}
\newcommand{\bisimv}[3]{\valuetyping{#1 \approx #2}{#3}}
\newcommand{\bisimr}[3]{\valuetyping{#1 \approx #2}{#3}}
\newcommand{\bisimF}[4]{\casttyping{#1 \approx #2}{#3}{#4}}
\newcommand{\bisimc}[4]{\casttyping{#1 \approx #2}{#3}{#4}}
\newcommand{\bisimK}[4]{\casttyping{#1 \approx #2}{#3}{#4}}
\newcommand{\bisims}[3]{\valuetyping{\ensuremath{#1 \approx #2}}{#3}}

\begin{document}
%
\title{A Framework for Equivalence of Cast Calculi and a new Cast Representation}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Kuang-Chen Lu\inst{1} \and
Jeremy G. Siek\inst{2} \and
Andre Kuhlenschmidt\inst{2}
}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Brown University, Providence RI 02912, USA \and
Indiana University, Bloomington IN 47405, USA}
% \institute{Princeton University, Princeton NJ 08544, USA \and
% Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
% \email{lncs@springer.com}\\
% \url{http://www.springer.com/gp/computer-science/lncs} \and
% ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
% \email{\{abc,lncs\}@uni-heidelberg.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Gradual typing aims at combining dynamic typing and static typing in one 
language to provide the advantages of both typing disciplines. Implementing 
gradual typing with reasonable overhead, however, is not trivial. Casts might 
accumulate in higher-order values and continuations, thus change the overall 
space complexity. Several space-efficient cast representations have been 
proposed, notably coercions in normal forms and threesomes. But they are
presented in different dynamic semantics, which make it difficult to compare
the key differences between the cast representations. We present a abstrat
data type, namely Cast ADT, that captures interface functions a cast representations
typically includes, and an abstract machine parameterized over Cast ADTs.
The Cast ADT brings another benefit: space-efficient cast representations 
shall be proved not changing the 
overall behavior of language implementations except saving space.
With our generic abstract machine, these proofs can be done by proving properties
of a specific Cast ADT, which is simpler than going through a bisimulation proof 
between a space-efficient dynamic semantics and the definitional dynamic semantics.
We have successfully applied our new approach of proving the correctness of cast 
representations to several known cast representations and believe this framework
is also applicable to other cast representations.
\todo[inline]{JS: cite which other cast representations}
\todo[inline]{KC: will do.}
We also present a new cast representation, hypercoercions, that is more friendly
to mechanized meta-theory and consumes less memory than coercions
in normal forms.

@@

\todo[inline]{KC: Cite "Contracts for higher-order functions" for the proxy-based approach maybe?}
\todo[inline]{JS: That paper doesn't exactly fit into what you're talking about in the above
sentence. It might be appopriate to cite it elsewhere in the paper. Also,
there are earlier papers about coercive subtyping (Computing with coercions by Breazu-Tannen et al)
that use a proxy-based approach. The contracts paper may be the first to propose blame tracking.}
\todo[inline]{KC: How about citing the origin of the proxy-based approach when we talk
about the CPSed even-odd example?
I am confused about which paper to cite. \cite{herman2010space} seems to be citing
\cite{findler2002contracts} for the proxy-based approach of casting function.
Here is the relevant sentences from \cite{herman2010space}:
``In general, it is not possible to check if an untyped function satisfies a
particular static type. A natural solution is to wrap the function in a proxy that, whenever
it is applied, casts its argument and result values appropriately, ensuring that the function
is only observed with its expected type. This proxy-based approach was formalized by Findler
and Felleisen [15] ...''
I am \textit{not} trying to say I don't believe in your statements about the origins of
the proxy-based approach and blame tracking in functions.
I want to know whether \citet{herman2010space} is citing the right paper.
Maybe both papers came up independently with a similar idea but \cite{findler2002contracts}
is more related to our work.
}

Gradual typing \citep{siek2006gradual,siek2015refined} includes both static typing 
and dynamic typing in the same language and enables a smooth transition between them while
enforcing type soundness.
To enable a smooth transition, gradually typed languages feature a special type
typically written as \Tdyn{}, \lstinline|Dyn|, or \lstinline|Any|, which
provides a way to write imprecise type annotations. A gradual type checker allows programmers to cast 
implicitly between types that have no conflicting type information.
At runtime, casts record and check type information to enforce type soundness.
Researchers often define the semantics of gradually typed languages by
translation to an intermediate language with explicit casts, such as the blame
calculus \citep{wadler2009well} and other cast calculi \citep{siek2009exploring}.

@@

\todo[inline]{KC: This paragraph suggests that
\cite{siek2009exploring} gives the definitional semantics.
\cite{siek2009exploring}'s is coercion-based.
It makes more sense to me to use a type-based semantics as the definition.
Actually in my mind \cite{siek2012interpretations} is definitional.}

@@

\subsection{Dynamics parameterized over cast representations}
\citet{siek2020mechanized} defines two dynamic semantics for 
cast calculi parameterized over cast representations. The first
semantics, namely CC, is \textit{not} space-efficient and
parameterized over $\mathrm{CastStruct}$. The author instantiates
CC to obtain the blame calculus ($\lambda B$). 
The resulting semantics is analogous to our \LUDMachine.
The other semantics, namely SC, is designed to be space-efficient
and parameterized over $\mathrm{EfficientCastStruct}$. SC is analogous
to our \SMachine{C}. These two parameterized semantics give
users more control over the structure of values. Our \CMachine{B} machine
insists that the cast on the top of a value must be a function cast
or a product cast. In contrast, users of their interfaces define
a predicate on casts called $\mathrm{Inert}$ and any inert cast can
be a part of a value. Their system doesn't include theorems relating
space-inefficient cast calculi and space-efficient ones, which
is one of the major goals of our framework.

@@

\todo[inline]{JS: The above is too short of a description of that related
work.}
\todo[inline]{KC: I am actually very confused by \citet{garcia2014deriving}.
They stated that ``Theorems 8.1 and 8.3 can be generalised for other choices
of dynamic semantics by applying the correspondence described
through the paper starting with a different set of coercion artefacts.''.
However they didn't give a generalization and it is unclear to me over what
their system is parameterized (cast representations? apply-coercion and seq?.}

\subsection{Correctness of cast representations}

\todo[inline]{JS: say something about the difference between the above
  and what is in this paper. That's the whole point of the related
  work section from the eyes of the reviewer.}
\todo[inline]{KC: I might have some misconcept about the related work section.
You might have felt this, haha. Now I think this section is targeting the
following scenarios: 
- ``I think someone has solved this problem ...''
- ``This work looks similar to paper X, what is the difference?''
- ``Is this work inspired by paper X?''
Is my understanding correct?}
\todo[inline]{JS: yes, and make sure to
  give very explicit answers to these questions. It should feel to you
  like you're hitting the reader over the head with the most obvious
  things (to you). The above paragraph is currently insufficient
  because it doesn't emphasize what scientific constributions are new
  to our paper compared to those prior papers on coercions in normal
  form.}
\todo[inline]{KC: I rewrote this section. Please check again.}

\citet{Siek:2010:TWB:1706299.1706342} introduce Lazy UD threesomes and
prove the correctness of Lazy UD threesomes. To use threesomes for
optimization, they define a translation from their cast calculus
(the blame calculus) to a runtime language (threesome calculus).
Then they define a bisimulation relation connecting the blame calculus
and the threesome calculus and prove a bisimulation between them.
In contrast, our \CMachine{B} is an interpreter of the cast calculus and 
compiles casts to cast representations on the fly.

\citet{Garcia:2013:CTB:2500365.2500603}
introduces several other flavors of threesomes, including a Lazy D
one. Their threesomes are derived from the corresponding styles of
coercions in \citet{herman2010space}, using correctness-preserving
transformation.

\cite{Siek:2015:BCT:2737924.2737968} proves the correctness
of \LUD\ coercions in normal form. Their approach is similar to
that of \citet{Siek:2010:TWB:1706299.1706342}. They defines
three calculi (i.e. $\lambda B$ (the blame calculus), $\lambda C$, and
$\lambda S$). $\lambda C$ uses coercions but doesn't normalize coercions
so is not space-efficient. $\lambda S$ uses coercions in normal form
and is space-efficient. To establish the correctness of $\lambda S$,
they prove a bisimulation relating $\lambda B$ to $\lambda C$
and a bisimulation relating $\lambda C$ to $\lambda S$.
Inspired by the approaches of \cite{Siek:2010:TWB:1706299.1706342}
and \cite{Siek:2015:BCT:2737924.2737968}, 
we also use the bisimulation technique.

@@

The syntax \error{l} occurs several times in the syntax definition. We shall 
view those nonterminals that have an \error{l} case as error monads. We use 
the symbol \mbind{} as the monad bind operator, which is defined as follows:
\[
\begin{array}{rcll}
(\error{l}) \mbind f & = & \error{l} \\
          a \mbind f & = & f(a)      & \text{otherwise}
\end{array}
\]
\todo[inline]{JS: why not use monadic let instead? That avoids
  the need to also use meta-lambdas, which you would need to
  explain, e.g., in the transition rule that uses applyCast.}
\todo[inline]{KC: 1. I will try to switch to monadic let. As you pointed out
when we wrote the WGT paper, let is more friendly to readers who are not familiar
with monads.
2. Do you imply that monadic let doesn't need to be explained?
}
\todo[inline]{JS: No, you should still define monadic let.}
\todo[inline]{KC: will do.}

@@

The transition relation \reduceto{s}{s} invokes the cast application
function, noted as $\applyCast{v}{\ccast{S}{l}{T}}$, which is also defined
by specify blame strategies (Fig.~\ref{fig:blame-strategy-LazyD} and
Fig.~\ref{fig:blame-strategy-LazyUD}).
\todo[inline]{JS: be consistent with the font used for applyCast. Sometimes
  you use roman and sometimes you used italic. Also, be consistent
  for all the metafunctions (eval, observe, etc.).}
\todo[inline]{KC: Fixed.}
%
When evaluating a cast expression, the machine moves the cast to the
continuation and evaluates the inner expression.
%
To cast a value, the machine invokes applyCast on the value. The cast
result is either a value or an error (\error{l}). If the cast
succeeds, the machine returns the value to the next continuation.  If
the cast fails, the machine halts with the blame label.
%
To apply a casted function, the machine first casts the argument $v$, then
applies the inner function $u$ to the casted argument, and finally
casts the return value.
%
To project the first element of a casted pair, the machine projects
the first element of the inner pair $u$ and cast it.
%
Projecting the second element of a casted pair is similar.

@@

\fbox{$\applyCastName_{\BLD}(v,\ccast{S}{l}{T}) = r$}
\[
\begin{array}{rclr}
\figequalto{
\applyCast{v}{\ccast{\Tdyn}{l}{\Tdyn}}
}{
	\just{v}
}{}
\figequalto{
\applyCast{v}{\ccast{P}{l}{\Tdyn}}
}{
	\just{\vdyn{P}{v}}
}{}
\figequalto{
\applyCast{\vdyn{P}{u}}{\ccast{\Tdyn}{l}{Q}}
}{
\applyCast{u}{\ccast{P}{l}{Q}}
}{}
\figequalto{
\applyCast{v}{\ccast{P}{l}{Q}}
}{
	\just{\proxy{v}{\ccast{P}{l}{Q}}}
}{\sidecond{\shallowlyconsistent{P}{Q}}}
\figequalto{
\applyCast{v}{\ccast{P}{l}{Q}}
}{
	\error{l}
}{\sidecond{\notshallowlyconsistent{P}{Q}}}
\end{array}
\]
\caption{The \LD\ blame strategy (\BLD)}
\label{fig:blame-strategy-LazyD}
\end{figure}

\todo[inline]{KC: conditions of blame strategy. Jeremy, please }
\begin{definition}[Blame Strategy, $B$]
A blame strategy defines a subset of pre-types, written I, that is injectable,
and a function, written \applyCastName, that applies cast to values.
\end{definition}

@@

Similarly, cases 4 and 5 of Lazy UD Cast ADT correspond to the fourth
case of Lazy UD \applyCastName (Fig.~\ref{fig:blame-strategy-LazyUD}).
Cases 7-9 correspond to the sixth case of
Lazy UD \applyCastName.

@@

\todo[inline]{JS: There should be some text regarding the following
two theorems.}
\todo[inline]{KC: will do}
